---
title: "Developing Data Products Week 4 Assignment"
author: "XH"
date: "5/15/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## INTRODUCTION

- To show a Shiny App that display plots of major European Stock Indices from 1991 to 1998 using the EuStockMarkets data set in R
- Users have the option to set two parameters:
       - Stock Index to display
       - Type of graph: Levels or Daily Differences

## SHINY APP: HOW IT WORKS

- User specify which index to display.  Have 5 options:  
       1. ALL: All indices  
       2. DAX  
       3. SMI  
       4. CAC  
       5. FTSE  
- User also specify what type of value to display in graph.  Two options:  
       1. LEVEL: Daily Closing Value  
       2. DAILY DIFFERENCES: The daily differences in closing value   
- Using these information, a plot is displayed

## EXAMPLE PLOT

- If DAX and LEVEL options are chosen, the following chart displays

```{r exampleplot}
data(EuStockMarkets)
EuStockMarkets <- EuStockMarkets[,1]
plot(EuStockMarkets, main='Plot of Stock Index Level', xlab='Date', ylab='Value')
```

## CONCLUSION

- Quick way for users to see evolution of stock indices over time 
- Shiny App is able to be adapted to include other stock indices and time periods
- Other types of graphs can be added to the Shiny App
